% \bibitem{}  (2021). . [online]. Available: \url{}. [Accessed 26 May. 2021].

\label{bib:1} \bibitem{1} U.S. Space Force (2021). GPS Accuracy. [online]. Available: \url{https://www.gps.gov/systems/gps/performance/accuracy/}. [Accessed 26 May. 2021].

\label{bib:2} \bibitem{2} Samuel K. Moore (2018). Superaccurate GPS Chips Coming to Smartphones in 2018. [online]. Available: \url{https://spectrum.ieee.org/tech-talk/semiconductors/design/superaccurate-gps-chips-coming-to-smartphones-in-2018}. [Accessed 26 May. 2021].

\label{bib:3} \bibitem{3} Real-time kinematic positioning. [online]. Available: \url{https://en.wikipedia.org/wiki/Real-time_kinematic_positioning}. [Accessed 26 May. 2021].

% 
\label{bib:4} \bibitem{4}  (2021). . [online]. Available: \url{}. [Accessed 26 May. 2021].
\label{bib:5} \bibitem{5}  (2021). . [online]. Available: \url{}. [Accessed 26 May. 2021].
\label{bib:6} \bibitem{6}  (2021). . [online]. Available: \url{}. [Accessed 26 May. 2021].



\label{bib:7} \bibitem{7} En.wikipedia.org. Motion capture. [online]. Available: \url{https://en.wikipedia.org/wiki/Motion_capture}. [Accessed 26 May. 2021].

\label{bib:8} \bibitem{8} Vicon.org. About Vicon. [online]. Available: \url{https://www.vicon.com/about-us/what-is-motion-capture/}. [Accessed 26 May. 2021].

\label{bib:9} \bibitem{9} Optitrack.org. Optitrack. [online]. Available: \url{https://optitrack.com/}. [Accessed 26 May. 2021].


\label{bib:10} \bibitem{10} Opencv.org. About Opencv. [online]. Available: \url{https://opencv.org/about/}. [Accessed 26 May. 2021].

\label{bib:11} \bibitem{11} Ros.org. About ROS. [online]. Available: \url{https://www.ros.org/about-ros/}. [Accessed 26 May. 2021].


